Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-01-24 Report/convergence_centralized.tex
modified

Let us express the \ac{JSFRA} problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
\begin{IEEEeqnarray}{rCl} \label{con}
\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mz) \eqsub \label{con-obj} \\
\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
&\quad& g_1(\mx,\my) \leq 0, \eqsub \label{con-cvx-blk} \\
&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx}
\end{IEEEeqnarray}
wher \me{g_2,f} are convex functions and \me{h} is a linear function. Let \me{g_0,g_1} are convex functions only on \me{\mx} or \me{\my} as the variable but not on both. Note that the \eqref{con-dc} correspond to the constraints in \eqref{eqn-6.2} and \eqref{eqn-mse-1.2} and \eqref{con-cvx-blk} corresponds to the constraints in \eqref{eqn-6.3} and \eqref{eqn-mse-1.3}. Other convex constraints are addressed by the constraint \eqref{con-cvx}. With this, the feasible set of the problem \eqref{con} is given by 
\begin{IEEEeqnarray}{rl}
\mc{F} &= \{ \mx,\my,\mz | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0\} \nonumber
\end{IEEEeqnarray}

In order to solve the problem, we resort to \ac{AO} by fixing a block of varibles and optimize for others. In the problem \eqref{con}, even after fixing the variable \me{\my}, the problem is nonconvex due to the \ac{DC} constraint in \eqref{con-dc}. In order to solve the problem after fixing the variable \me{\my}, we adopt the \ac{SCA} approach presented in \cite{lipp2014variations,lanckriet2009convergence,scutari_1} by relaxing the nonconvex set by a sequence of convex subsets. Since the proposed method involves two level of iterations, we denote the \ac{AO} iteration index by a superscript \me{(i)} and the \ac{DC} constraint relaxations by a subscript \me{k}. Let \me{\iter{\mc{X}}{k}{i}} be a feasible set for the \eqn{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for a fixed \me{\my} and for a fixed \me{\mx}, the set is represented as \me{\iter{\mc{Y}}{k}{i}}. Since the \ac{SCA} iterations are performed until convergence, let \me{\iter{\mx}{\ast}{i}} denotes the converged point of \me{\mx} in the \me{\ith{i}} \ac{AO} iteration.

Without affecting the convergence proof, let us consider the variable \me{\my} is fixed in the iteration \me{i} for \ac{AO} and \me{k} for the \ac{SCA} problem to solve for the unique minimizer for \me{\mx \in \iter{\mc{X}}{k}{i}}.

In order to solve for a suboptimal solution, let us resort to the \ac{AO} by fixing a block of variables and optimize for others. Before proceeding further, let us define the following notations. Let \me{\iter{\mx}{k}{i}} denote the \me{\ith{i}} \ac{AO} operating point and \me{k} represent the \me{\ith{k}} \ac{SCA} point. Let us define a set \eqn{\iter{\mc{X}}{k}{i}} as set of feasible values of the subproblem in the \me{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} optimization point for a fixed variable \me{\my}. Since \ac{AO} is an iterative method, let us begin by fixing \me{\my} with the previously found optimal value \me{\iter{\myb}{\ast}{i-1} \in \iter{\mc{Y}}{\ast}{i-1} \subset \mc{F}}, where \me{\ast} in subscript denotes the optimal value over some set \me{\mc{Y}}. Now the problem in \eqref{con} is still nonconvex due to the constraint \eqref{con-dc}, which is in \ac{DC} form. Following the approaches presented in \cite{lipp2014variations,lanckriet2009convergence,scutari_1}, the function \me{g_0(\mx,\iter{\myb}{\ast}{i-1})} is linearized around a fixed feasible point \me{\iter{\mxb}{\ast}{i} \in \iter{\mc{X}}{\ast}{i-1} \subset \mc{F}} by
\begin{equation} \label{con-relax}
\hat{g}_o(\mx,\iter{\myb}{\ast}{i-1});\iter{\mx}{k}{i})) = {g}_0(\iterate{\mxb}{0},\iterate{\myb}{0}) + \nabla g_0(\iterate{\mxb}{0},\iterate{\myb}{0})^\mathrm{T} (\mx - \iterate{\mxb}{0}).
Using the relaxation \eqref{con-relax}, the convex subproblem for the \me{\ith{i}} \ac{AO} iterate of \me{\myb} and the \me{\ith{k}} linear approximation of \me{\mxb} as

@@

	\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mz) \eqsub \label{con-obj-m} \\
	\text{subject to} &\quad& h(\mz) - \hat{g}_0(\mx,\iterate{\myb}{i};\iterate{\mxb}{k}) \leq 0 \eqsub \label{con-dc-m} \\
	&\quad& g_1(\mx,\iterate{\myb}{i}) \leq 0, \eqsub \label{con-cvx-blk-m} \\

@@

Let the set defined by the problem in \eqref{con-relax} be represented as \me{\iterate{\mc{X}}{i}_{k} \subset \mc{F}}, where \me{\mc{X}} denotes the subset in which \me{\my} is fixed. In order to prove the convergence of the convex subproblem \eqref{con-m} for a fixed \me{\iterate{\myb}{i}} and \me{\iter{\mxb}{k}{i}}, let us assume that \eqref{con-m} yields \me{\mx_{k+1}} and \me{\mz_{k+1}} as the solution at the \me{\ith{k}} iteration. To show that \me{\mx_{k+1}} and \me{\mz_{k+1}} minimizes the objective function ans also feasible, let us assume that the point \me{\iterate{\mxb}{k}} is feasible for \eqref{con-m}. Since the function \me{{g}_0(\mx,\iterate{\myb}{i})} is linearized around \me{\iterate{\mxb}{k}}, it satisfies

@@

h(\mz) - {g}_0(\mx,\iterate{\myb}{i}) \leq h(\mz) - \hat{g}_0(\mx,\iterate{\myb}{i};\mxb_k) \leq 0,

@@

since \me{{g}_0(\mx,\iterate{\myb}{i}) \leq \hat{g}_0(\mx,\iterate{\myb}{i};\mxb_k), \forall \mx \in \iterate{\mc{X}}{i}_{k-1}}. Now, \me{\mx_{k+1}} is the solution and feasible for the \me{\ith{k}} subproblem, therefore, it satisfies
\begin{multline}
h(\mz_{k+1}) - {g}_0(\mx_{k+1},\iterate{\myb}{i}) \leq h(\mz_{k+1}) - \hat{g}_0(\mx_{k+1},\iterate{\myb}{i};\mxb_k) \\
\leq h(\mz_{k}) - \hat{g}_0(\mx_{k},\iterate{\myb}{i};\mxb_k) \leq 0. \label{con-sub-set}

@@

Using \eqref{con-sub-set}, we can prove that the solution \me{\mx_{k+1}} and \me{\mz_{k+1}} are feasible, since the initial point \me{\mx_{0}} was chosen to be feasible. In order to prove the convergence of the objective, using \eqref{con-sub-set}, we can see that \me{\iterate{\mc{X}}{i}_{0} \subseteq \dots \subseteq \iterate{\mc{X}}{i}_{k-1} \subseteq \iterate{\mc{X}_k}{i} \subset \mc{F}}. Since at \me{\ith{k}} iteration, the feasible set of the problem \eqref{con-m} includes the feasible sets of the earlier iteration, we can see that 
\begin{equation} \label{con-convergence}
f(\mz_0) \geq f(\mz_k) \geq f(\mz_{k+1}) \geq f(\mz_{\ast,x,i}). 
Thus the sequence \me{f(\mz_k)} is nonincreasing and converges to a critical point. Let \me{\mx_{\ast}} and \me{\mz_{\ast,x,i}} be the optimal point of the problem \eqref{con-m} when the iterative algorithm is converged. The symbol \me{x,i} in \me{\mz_{\ast,x,i}} denotes the optimal \me{\mz} is found over the variable \me{\mx} at the \eqn{\ith{i}} \ac{AO} iteration. Note that this point need not be a stationary point of the problem \eqref{con}, since it is the minimizer only in the feasible set \me{\iterate{\mc{X}_{\ast}}{i} \subset \mc{F}}, which depend on \me{\mx} only.

Once the solution is found for a fixed \me{\my}, we fix \me{\mx} as \me{\iterate{\mxb}{i} = \mx_{\ast}} and optimize for \me{\my}. The problem is still nonconvex due to the \ac{DC} constraint. By following similar approach, we can obtain the minimizer \me{\my_{k}} for the convex subproblem at each iteration \me{{k}}. The convergence and the nonincreasing behavior of the problem follows similar arguments as above. Now, the optimal solution of the converged subproblem with \me{\my} as variable is \me{\my_{\ast}} and \me{\mz_{\ast,y,i}}. Note that the solution \me{\mz_{\ast,y,i}} is the minimizer in the subset \me{\iterate{\mc{Y}_{\ast}}{i}}.

Finally, to prove the global convergence of the objective, we need to show the nonincreasing behavior of the objective function between each \ac{AO} update, \textit{i.e}, \me{f_0(\mz_{\ast,x,i}) \geq f_0(\mz_{\ast,y,i}) \geq f_0(\mz_{\ast,x,i+1})}. Let us consider the \ac{AO} iteration \me{i} in which the optimal value for \eqn{\mx} and \eqn{\mz} is obtained as \eqn{\mx^{(i)}_{\ast}} and \eqn{\mz_{\ast,x,i}} using a fixed \eqn{\my} as \eqn{\my_{\ast}^{(i-1)}}. In order to find \eqn{\iter{\my}{\ast}{i}}, we fix \eqn{\mx} as \eqn{\iter{\mx}{\ast}{i}} and optimize for \me{\my}. Since the problem \eqref{con} is nonconvex even after fixing \me{\mx}, we have to linearize the convex function in the \ac{DC} constraint \eqref{con-dc} around some fixed operating point of \me{\my}. Since the linearization is performed with the earlier optimal point \eqn{\iter{\my}{\ast}{i-1}}, the feasible set now includes \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i}\} \in \mc{Y}^{(i)}_{0}}. Now the optimization is performed to find the optimal \me{\my} using the relaxed problem \eqref{con-m}, the optimal solution \me{\mz_{0,y,i}} for the initial iteration after \ac{AO} update follows \me{f_0(\mz_{0,y,i}) \leq f_0(\mz_{\ast,x,i})}, since the feasible set includes the earlier optimal points \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i}\}}. Note that it is not possible to say \me{\iter{\mc{X}}{\ast}{i} \subseteq \iter{\mc{Y}}{0}{i}} since the set is nonconvex on \me{\mx,\my}, but \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}}. Now by using induction, we can show that the global problem converges to a feasible point of the nonconvex problem \eqref{con} in a nonincreasing manner.

To show the converged point of the iterative algorithm is in fact the stationary point of the nonconvex problem \eqref{con}, it must satisfy the \ac{KKT} conditions of the nonconvex problem. Since the converged point is the minimizer for the iterative algorithm such that 
\begin{equation} \label{con-opt}
f_0(\mz_{\ast,x,i}) = f_0(\mz_{\ast,y,i}) = f_0(\mz_{\ast,x,i+1}),
\end{equation}
the solution is inside the feasible set \me{\mc{F}} and \me{\mz_{\ast,x,i+1}} is the minimizer of the objective function \me{f_0} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}, which includes all optimal points of \me{\mz} identified so far. Using the discussions in \cite{marks1978technical}, we can easily show that the feasible point \me{\mz_{\ast,x,i+1}} is a stationary point of the non convex problem in \eqref{con} satisfying the constraint qualifications and the \ac{KKT} expressions for the set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}. The non differentiability of the objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} requires the subdifferential set of the objective function to include \me{0 \in \partial f_0(\mz_{\ast})} to satisfy the \ac{KKT} conditions.

Note that the uniqueness of the convex subproblems \eqref{con-m} is required for the convergence of \ac{AO}. We can prove the uniqueness of the convex subproblems defined by \eqref{eqn-9} and \eqref{eqn-mse-2} using the following constraints. For the problem \eqref{eqn-9}, the uniqueness of the transmit precoders is guaranteed by the constraint \eqref{eqn-8}, which can be written as
\begin{multline}
\gamma_{l,k,n} + \tilde{\beta}_{l,k,n}^{-2} |\mvec{\tilde{H}}{b_k,k,n} \mvec{\tilde{m}}{l,k,n}|^2 (\beta_{l,k,n} - \tilde{\beta}_{l,k,n}) \\
- \tilde{\beta}_{l,k,n}^{-1} \mvec{\tilde{m}}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n} (\mvec{m}{l,k,n} - \mvec{\tilde{m}}{l,k,n}) \leq 0,
\end{multline}
where \eqn{\mvec{\tilde{H}}{b_k,k,n} = \mvec{w}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}} and for the convex subproblem \eqref{eqn-mse-2}, uniqueness of the transmit precoder is guaranteed by the constraint 
\begin{multline}
| 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} |^2 \\ + \sum_{\mathclap{(j,i) \neq (l,k)}} | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 + \enoise \leq \epsilon_{l,k,n}.
\end{multline}
Using these arguments, we can claim that the proposed \ac{JSFRA} centralized solution achieves a stationary point of the original nonconvex problem with the nonincreasing objective value at each iteration.

>>>>

Let us express the \ac{JSFRA} problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
\begin{IEEEeqnarray}{rCl} \label{con}
\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mx,\my,\mz) \eqsub \label{con-obj} \\
\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
&\quad& g_1(\mx,\my) \leq 0, \eqsub \label{con-cvx-blk} \\
&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx}
\end{IEEEeqnarray}
wher \me{g_2,f} are convex functions and \me{h} is a linear function. Let \me{g_0,g_1} are convex functions only on \me{\mx} or \me{\my} as the variable but not on both. Note that the \eqref{con-dc} correspond to the constraints in \eqref{eqn-6.2} and \eqref{eqn-mse-1.2} and \eqref{con-cvx-blk} corresponds to the constraints in \eqref{eqn-6.3} and \eqref{eqn-mse-1.3}. Other convex constraints are addressed by the constraint \eqref{con-cvx}. With this, the feasible set of the problem \eqref{con} is given by 
\begin{IEEEeqnarray}{rl}
\mc{F} &= \{ \mx,\my,\mz | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0\} \nonumber
\end{IEEEeqnarray}

In order to solve the problem, we resort to \ac{AO} by fixing a block of varibles and optimize for others. In the problem \eqref{con}, even after fixing the variable \me{\my}, the problem is nonconvex due to the \ac{DC} constraint in \eqref{con-dc}. In order to solve the problem after fixing the variable \me{\my}, we adopt the \ac{SCA} approach presented in \cite{lipp2014variations,lanckriet2009convergence,scutari_1} by relaxing the nonconvex set by a sequence of convex subsets. Since the proposed method involves two level of iterations, we denote the \ac{AO} iteration index by a superscript \me{(i)} and the \ac{DC} constraint relaxations by a subscript \me{k}. Let \me{\iter{\mc{X}}{k}{i}} be a feasible set for the \eqn{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for a fixed \me{\my} and for a fixed \me{\mx}, the set is represented as \me{\iter{\mc{Y}}{k}{i}}. Since the \ac{SCA} iterations are performed until convergence, let \me{\iter{\mx}{\ast}{i}} denotes the converged point of \me{\mx} in the \me{\ith{i}} \ac{AO} iteration. For the sake of clarity, we define the optimal value of \me{\mz} obtained for the \me{\ith{i}} \ac{AO} iterate for the fixed \me{\my} variable as \me{\iter{\mz}{\ast|y}{i}}.

Let us consider the order for \ac{AO} by optimizing variable \me{\mx} before optimizing the variable \me{\my}. Without affecting the convergence proof, let us consider the variable \me{\my} is fixed for the \ac{AO} \me{i} with the optimal value achieved from the previous iteration \me{i-1} as \me{\iter{\my}{\ast}{i-1}}. In order to find the optimal value of \me{\mx} for the \ac{SCA} iteration \me{k}, we linearize the nonconvex function \me{g_0} using previous \ac{SCA} iterate of \me{\mx} as
\begin{multline} \label{con-relax}
\hat{g}_o(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) = {g}_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1}) \\ + \nabla g_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1})^{\mathrm{T}} (\mx - \iter{\mx}{k}{i}).
Using \eqref{con-relax}, the convex subproblem for \me{\ith{i}} \ac{AO} iteration and \me{\ith{k}} \ac{SCA} point for the variable \me{\mx} and \me{\mz} is given by

@@

	\underset{\mx,\mz}{\text{minimize}} &\quad& f(\mx,\iter{\my}{\ast}{i-1},\mz) \eqsub \label{con-obj-m} \\
	\text{subject to} &\quad& h(\mz) - \hat{g}_0(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0 \eqsub \label{con-dc-m} \\
	&\quad& g_1(\mx,\iter{\my}{\ast}{i-1}) \leq 0, \eqsub \label{con-cvx-blk-m} \\

@@

Let the set defined by the problem in \eqref{con-m} be represented as \me{\iter{\mc{X}}{k}{i} \subset \mc{F}}. In order to prove the convergence of the convex subproblem \eqref{con-m} for a fixed \me{\my = \iter{\my}{\ast}{i-1}} operating at \me{\iter{\mx}{k}{i}}, let us assume that \eqref{con-m} yields \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} as the solution at the \me{\ith{k}} iteration. To show \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} minimizes the objective function ans also feasible, let us assume that the point \me{\iter{\mx}{k}{i} \in \iter{\mc{X}}{k}{i}}, which is feasible for \eqref{con-m}. Since the function \me{{g}_0(\mx,\iter{\my}{\ast}{i-1}} is linearized at \me{\iter{\mx}{k}{i}}, it satisfies

@@

h(\mz) - {g}_0(\mx,\iter{\my}{\ast}{i-1}) \leq h(\mz) - \hat{g}_0(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0,

@@

since \me{{g}_0(\mx,\iter{\my}{\ast}{i-1}) \leq \hat{g}_0(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}), \forall \mx \in \iter{\mc{X}}{k}{i}}. Now, \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} are the optimal and feasible point for the \me{\ith{k}} subproblem \eqref{con-m}, it satisfies
\begin{multline}\label{con-sub-set}
h(\iter{\mz}{k+1}{i}) - {g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1}) \leq h(\iter{\mz}{k+1}{i}) - \hat{g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \\
\leq h(\iter{\mz}{k}{i}) - \hat{g}_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0. 

@@

Using \eqref{con-sub-set}, we can prove that the solution \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} are feasible, since the initial point of \me{\mx = \iter{\mx}{\ast}{i-1}} was chosen to be feasible from the earlier \ac{AO} iteration \me{i-1}. In order to prove the convergence of the objective, using \eqref{con-sub-set}, we can see that \me{\iter{\mc{X}}{0}{i} \subseteq \dots \subseteq \iter{\mc{X}}{k-1}{i} \subseteq \iter{\mc{X}}{k}{i} \subset \mc{F}}. Since the feasible set of the problem \eqref{con-m} includes the feasible sets from the earlier iteration, we arrive at
\begin{multline} \label{con-convergence}
f(\iter{\mx}{0}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{0}{i}) \geq f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i}) \\ \geq f(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}) \geq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i}). 
Thus the sequence \me{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})} is nonincreasing and converges to a critical point. Note that feasible point \me{(\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i})} need not be a stationary point of the problem \eqref{con}, since it is the minimizer only in the feasible set \me{\iter{\mc{X}}{\ast}{i} \subset \mc{F}}, which depends on \me{\mx} and \me{\mz} only.

Once the solution is found for a fixed \me{\my}, we fix \me{\mx} as \me{\iter{\mx}{\ast}{i}} and optimize for \me{\my}. Even after treating \me{\mx} as a constant, the problem is still nonconvex due to the \ac{DC} constraint. Following similar approach, we can find the minimizer \me{\iter{\my}{k}{i}} and \me{\iter{\mz}{k}{i}} for the convex subproblem \eqref{con-m} at each iteration \me{{k}}. Note that \me{\iter{\mz}{k}{i}} is reused since the variable \me{\mx} is fixed for the \me{\ith{i}} \ac{AO} iteration. The convergence and the nonincreasing behavior of the problem follows similar arguments as above. Now, the optimal solution of the converged subproblems with \me{\my} as variable are \me{\iter{\my}{\ast}{i}} and \me{\iter{\mz}{\ast}{i}}. Note that the solution point \me{(\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i})} is the unique minimizer in the set \me{\iter{\mc{Y}}{\ast}{i}}.

Finally, to prove the global convergence of the objective, we need to show the nonincreasing behavior of the objective function between each \ac{AO} update, \textit{i.e}, 
\begin{equation*}
f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i}).
\end{equation*}
Let us consider an \ac{AO} iteration \me{i} in which the optimal value for \eqn{\mx} and \eqn{\mz} are obtained as \me{\iter{\mx}{\ast}{i}} and \me{\iter{\mx}{\ast|y}{i}} using fixed \eqn{\my = \iter{\my}{\ast}{i-1}}. In order to find \me{\iter{\my}{\ast}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\ast}{i}} and optimize for \me{\my}. Since the problem \eqref{con} is nonconvex even after fixing \me{\mx}, we have to linearize the convex function in the \ac{DC} constraint \eqref{con-dc} around some fixed operating point of \me{\my}. Since we know that \me{\iter{\my}{\ast}{i-1}} is already a feasible point for \me{\my} along with \me{\iter{\mx}{\ast}{i}}, linearization is performed around this feasible point. Using the inequality in \eqref{con-sub-set}, we can show that \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \iter{\mc{Y}}{0}{i}}. Now the optimization is performed to find the optimal \me{\my} using the relaxed subproblem \eqref{con-m}, the optimal solution \me{\iter{\mz}{0}{i}} for the initial iteration after \ac{AO} update follows
\begin{equation*}
f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|x}{i}),
\end{equation*}
since the feasible set includes the earlier optimal points \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i}\}} as the operating point for \ac{AO} and \ac{SCA} iteration. Note that it is not possible to say \me{\iter{\mc{X}}{\ast}{i} \subseteq \iter{\mc{Y}}{0}{i}}, since the set is nonconvex on \me{\mx,\my}, but \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}}. Now by using induction, we can show that the global problem converges to a feasible point of the nonconvex problem \eqref{con} in a nonincreasing manner.

To show the converged point of the iterative algorithm is in fact the stationary point of the nonconvex problem \eqref{con}, it must satisfy the \ac{KKT} conditions of the nonconvex problem. Since the converged point is the minimizer for the iterative algorithm such that 
\begin{multline} \label{con-opt}
f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) = f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i},\iter{\mz}{\ast|y}{i+1}) \\ = 
f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}),
\end{multline}
the solution is inside the feasible set \me{\mc{F}} and \me{(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})} is the minimizer of the objective function \me{f_0} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}. Using the discussions in \cite{marks1978technical}, we can easily show that the feasible point \me{\mc{F}} and \me{(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})}, which is the minimizer in the local neighborhood, is a stationary point of the non convex problem in \eqref{con} satisfying the constraint qualifications and the \ac{KKT} expressions for the set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}. The non differentiability of the objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} requires the subdifferential set of the objective function to include \me{0 \in \partial f_0(\mz_{\ast})} to satisfy the \ac{KKT} conditions.

The uniqueness of the convex subproblems \eqref{con-m} is required for the convergence of \ac{AO}. For the problem \eqref{eqn-9}, the uniqueness of the transmit precoders are guaranteed by the constraint \eqref{eqn-8}, which can be written as
\begin{multline}
\gamma_{l,k,n} + \tilde{\beta}_{l,k,n}^{-2} |\mvec{\tilde{H}}{b_k,k,n} \mvec{\tilde{m}}{l,k,n}|^2 (\beta_{l,k,n} - \tilde{\beta}_{l,k,n}) \\
- \tilde{\beta}_{l,k,n}^{-1} \mvec{\tilde{m}}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n} (\mvec{m}{l,k,n} - \mvec{\tilde{m}}{l,k,n}) \leq 0,
\end{multline}
where \eqn{\mvec{\tilde{H}}{b_k,k,n} = \mvec{w}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}} and for the \eqref{eqn-mse-2} by
\begin{multline}
| 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} |^2 \\ + \sum_{\mathclap{(j,i) \neq (l,k)}} | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 + \enoise \leq \epsilon_{l,k,n}.
\end{multline}
Using these arguments, we can claim that the proposed \ac{JSFRA} centralized solution achieves a stationary point of the original nonconvex problem with the nonincreasing objective value at each iteration.

### 2015-01-24 Report/ieee_journal.tex
manosha
modified

\documentclass[10pt,final,twocolumn,letterpaper]{./../Styles/IEEEtran}

\usepackage{amsmath,amssymb}
\usepackage{acronym,etoolbox}
\usepackage[ruled]{algorithm2e}
\usepackage[dvipdfmx]{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[subrefformat=parens,labelformat=parens,labelseparator=period,caption=false]{subfig}
\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,lineno,verbatim,todonotes,inputenc,mathtools}

>>>>

\documentclass[10pt,final,twocolumn,a4paper]{./../Styles/IEEEtran}

\usepackage{amsmath,amssymb}
\usepackage{acronym,etoolbox}
\usepackage[ruled]{algorithm2e}
\usepackage[dvips]{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[subrefformat=parens,labelformat=parens,labelseparator=period,caption=false]{subfig}
\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,lineno,verbatim,mathtools}
